Enforced Invariant Confluence

### 2018-03-11 doc/paper_redux/stratified_iconfluence.tex
Added another small TODO.
Modified stratified iconfluence execution.

This is unfortunate, but if we're determined to make $O$ \sTIconfluent{}? Well,
then we have to adjust the set of $\sTIreachable{}$ points so that they are a
subset of $I$. We can go about this in three ways:
\begin{itemize}
  \item \textbf{Adjust $s_0$.}
    $O$ is not \sticonfluent{(-2, 2)}{T}{I}, but it is \sticonfluent{(0,
    0)}{T}{I}. Thus, we can change our start state to become
    invariant-confluent. This is illustrated in \figref{FixingIconfluenceS}.

@@

Consider a state-based object $O = (S, \join)$, a start state $s_0$, a set of
transactions $T$, and an invariant $I$ deployed on $n$ processors $p_1, \ldots,
p_n$. Further assume that $O$ is a semilattice.
%
With stratified invariant-confluence, we construct an ordered sequence $P =
(I_1, T_1), \ldots, (I_n, T_n)$ of $n$ pairs $(I_i, T_i)$ with the following
properties:
\begin{itemize}
  \item
    $I_i \subseteq I$ for $1 \leq i \leq n$

@@

  \item
    $I = \cup_{i=1}^n I_i$

  \item
    For all $(I_i, T_i) \in P$ and all states $s \in I_i$, $O$ is
    \sticonfluent{s}{I_i}{T_i}.
\end{itemize}
All processors store a copy of $P$. Moreover, at any given point in time, a
processor $p_i$ will execute with one pair $(I_j, T_j) \in P$ \defword{active}.
We'll describe what this means in just a moment. Initially, every processor
$p_i$ is state $s_0$. $p_i$ finds the first pair $(I_j, T_j) \in P$ such that
$I_j(s_0)$ and makes this $(I_j, T_j)$ active. As usual, a processor can
perform one of two actions: execute a transaction or perform a merge.
\begin{itemize}
  \item
    Merging proceeds as usual. When a process $p_i$ with state $s_i$ receives a
    state $s_j$ from $p_j$, it transitions from $s_i$ to $s_i \join p_j$.

  \item
    Transaction processing is a bit different. Imagine a processor $p_i$ in
    state $s_i$ with pair $(I_j, T_j)$ active wants to execute transaction $t$.
    %
    If $t \in T_j$, then $p_i$ executes $t_i$ so long as doing so maintains
    $I_j$.
    %
    If $t \notin T_j$, then $p_i$ initiates a round of coordination among the
    processors. All processors adopt state state $s = s_1 \join \cdots \join
    s_n$. Then, all processors execute $t$. If $t(s)$ does not satisfy $I$,
    then the processors remain in state $s$ and continue normal processing.  If
    $t(s)$ does satisfy $I$, then the processors enter state $t(s)$ and choose
    pair $(I_k, T_k)$ to active where $(I_k, T_k)$ is the first pair in $P$
    where $I_k(t(s))$ (which is guaranteed to exist since $\cup_i I_i = I$).
\end{itemize}

@@

\todo{%
  Give name to things like $P$. Call it something like an $(I, T)$-partition.
}
\todo{Can we modify the decision procedure to help build a stratification?}

>>>>

This is unfortunate, but what if we're determined to make $O$ \sTIconfluent{}?
Well, then we have to adjust the set of $\sTIreachable{}$ points so that they
are a subset of $I$. We can go about this in three ways:
\begin{itemize}
  \item \textbf{Adjust $s_0$.}
    $O$ is not \sticonfluent{(-2, 2)}{T}{I}, but it is \sticonfluent{(0,
    0)}{T}{I}. Thus, we can change our start state to become
    invariant-confluent. This is illustrated in \figref{FixingIconfluenceS}.

@@

Consider a state-based object $O = (S, \join)$, a start state $s_0$, a set of
transactions $T$, and an invariant $I$ deployed on $n$ processors $p_1, \ldots,
p_n$. Further assume that $O$ is a semilattice.
%
With stratified invariant-confluence, we construct an \ITpartition{}: an
ordered sequence $P = (I_1, T_1), \ldots, (I_n, T_n)$ of $n$ pairs $(I_i, T_i)$
with the following properties:
\begin{itemize}
  \item
    $I_i \subseteq I$ for $1 \leq i \leq n$

@@

  \item
    $I = \cup_{i=1}^n I_i$ (note that the $I_i$'s don't have to be disjoint)

  \item
    For all $(I_i, T_i) \in P$ and all states $s \in I_i$, $O$ is
    \sticonfluent{s}{I_i}{T_i}.
\end{itemize}
All processors store a copy of the \ITpartition{} $P$. Moreover, at any given
point in time, a processor $p_i$ will execute with one pair $(I_j, T_j) \in P$
\defword{active}. We'll describe what this means in just a moment. Initially,
every processor $p_i$ is state $s_0$. $p_i$ finds the first pair $(I_j, T_j)
\in P$ such that $I_j(s_0)$ and makes this $(I_j, T_j)$ active. As usual, a
processor can perform one of two actions: execute a transaction or perform a
merge.
\begin{itemize}
  \item
    Merging proceeds as usual. When a process $p_i$ with state $s_i$ receives a
    state $s_j$ from $p_j$, it transitions from $s_i$ to $s_i \join p_j$.

  \item
    Transaction processing is a bit different. Imagine a processor $p_i$ in
    state $s_i$ with pair $(I_j, T_j)$ active wants to execute transaction $t$.

    If $t \in T_j$, then $p_i$ executes $t$ to transition from state $s_i$ to
    state $t(s_i)$. If $I_j(t(s_i))$, then $p_i$ returns to the client
    immediately. If $\lnot I(t(s_i))$, then $p_i$ aborts the transaction and
    returns to the client immediately. If $\lnot I_j(t(s_i))$ and $I(t(s_i))$,
    then $p_i$ initiates a round of global coordination among the processors,
    as described below.  If $t \notin T_j$, then $p_i$ also initiates a round
    of coordination.

    During a global coordination, all processors adopt state state $s = s_1
    \join \cdots \join s_n$. Then, all processors execute $t$. If $t(s)$ does
    not satisfy $I$, then the processors remain in state $s$ and continue
    normal processing.  If $t(s)$ does satisfy $I$, then the processors enter
    state $t(s)$ and choose pair $(I_k, T_k)$ to be active where $(I_k, T_k)$
    is the first pair in $P$ where $I_k(t(s))$ (which is guaranteed to exist
    since $\cup_i I_i = I$).
\end{itemize}

@@

\todo{%
  Give more examples where stratified invariant-confluence is helpful.
}
\todo{%
  Give name to things like $P$. Call it something like an $(I, T)$-partition.
}
\todo{Can we modify the decision procedure to help build a stratification?}
